A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-08-23 rr-flow.Rmd
fix starttoc
execute code in different R Versions
resolves #4

floatsintext      : yes
figurelist        : yes
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if(!require("pacman"))install.packages("pacman")
pacman::p_load("here", "tidyverse")
```

@@

```{bash, eval=FALSE}
docker run --rm rocker/r-ver:3.5.0 Rscript -e "set.seed(1234);sample(1:10, 5)"
```

@@

```{bash, eval=FALSE}
docker run --rm rocker/r-ver:3.6.0 Rscript -e "set.seed(1234);sample(1:10, 5)"
```

>>>>

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if(!require("pacman"))install.packages("pacman")
pacman::p_load("here", "tidyverse")

knitr::read_chunk(here("R", "random.R"))
```

@@

```{r random, eval=FALSE}
```

```{r, child="R/random35.md"}
```

@@

```{r random, eval=FALSE}
```

```{r, child="R/random36.md"}
```
